Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design

### 2016-10-06 MSR-design.tex
I've never heard this part of the reactor called anything except the 'downcomer'
neutron mesh -> neutronics mesh

A cutaway diagram of the \gls{MSRE} reactor is shown in \cref{fig:MSRE_reactor}. Fuel
enters through the inlet and is distributed evenly along the outside of the
reactor vessel in a small annular region of 1 inch
width \cite{robertson_msre_1965}. The fluid fuel then flows turbulently
downward, cooling the reactor vessel to within 5\textdegree F of the entering
bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. Some \gls{MSRE}
modeling papers (\cite{kophazi_development_2009}) refer to this down-flowing
region as the \textit{downcomer}. The fuel salt is collected in the lower plenum
(lower \textit{space}) of the reactor where straightening vanes remove the
salt's rotational motion. The salt then flows upward through approximately 1140
0.4-inch by 1.2-inch fuel channels that are formed by machining grooves in the
sides of the graphite moderator columns \cite{robertson_msre_1965}; these are the
regions where fission occurs. The graphite columns themselves have 2-inch by
2-inch square cross sections. Nominal core volume is 90 ft$^3$, with 70 ft$^3$
occupied by graphite and 20 ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
After flowing through the core channels, the fuel collects in the upper plenum
before exiting through the outlet.

@@

Neutron and thermal calculations are performed on separate grids. The axial and
horizontal neutron grids are both shown in \cref{fig:neutron-grid}. It includes
regions for the lower and upper salt plena, downcomer, and three control rods. A
section of the horizontal thermal grid is shown in \cref{fig:thermal-grid}. In
general, the thermal grid is finer than the neutron grid. Thermal and neutronic
calculations are coupled in the following way. Each cell of the neutron mesh
(containing both fuel and moderator, recall \cref{fig:kophazi_homo}) is
considered to have uniform cross-sections. To generate these constant
cross-sections in each neutronic cell, the fine-mesh temperature fields from
the thermal calculation (called THERM) are spatially averaged using an auxiliary
program. This averaged neutron-cell-specific temperature is then used in
conjunction with cross section interpolation tables generated by SCALE to
determine the macroscopic cross sections for each neutron cell in the
simulation.

>>>>

A cutaway diagram of the \gls{MSRE} reactor is shown in \cref{fig:MSRE_reactor}. Fuel
enters through the inlet and is distributed evenly along the outside of the
reactor vessel in a small annular region of 1 inch
width \cite{robertson_msre_1965}. The fluid fuel then flows turbulently 
downward, cooling the reactor vessel to within 5\textdegree F of the entering 
bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. This 
down-flowing region is typically referred to as the \textit{downcomer}. The 
fuel salt is collected in the lower plenum (lower \textit{space}) of the 
reactor where straightening vanes remove the salt's rotational motion. The salt 
then flows upward through approximately 1140 0.4-inch by 1.2-inch fuel channels 
that are formed by machining grooves in the sides of the graphite moderator 
columns \cite{robertson_msre_1965}; these are the regions where fission occurs. 
The graphite columns themselves have 2-inch by 2-inch square cross sections. 
Nominal core volume is 90 ft$^3$, with 70 ft$^3$ occupied by graphite and 20 
ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
After flowing through the core channels, the fuel collects in the upper plenum
before exiting through the outlet.

@@

Neutron and thermal calculations are performed on separate grids. The axial and
horizontal neutron grids are both shown in \cref{fig:neutron-grid}. It includes
regions for the lower and upper salt plena, downcomer, and three control rods. A
section of the horizontal thermal grid is shown in \cref{fig:thermal-grid}. In
general, the thermal grid is finer than the neutron grid. Thermal and neutronic
calculations are coupled in the following way. Each cell of the neutronics mesh
(containing both fuel and moderator, recall \cref{fig:kophazi_homo}) is
considered to have uniform cross-sections. To generate these constant
cross-sections in each neutronic cell, the fine-mesh temperature fields from
the thermal calculation (called THERM) are spatially averaged using an auxiliary
program. This averaged neutron-cell-specific temperature is then used in
conjunction with cross section interpolation tables generated by SCALE to
determine the macroscopic cross sections for each neutron cell in the
simulation.
